RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R

### 2014-06-24 manuscripts/manuscript.Rmd
removed fluff about "the next generation of phylogenetic informatics data"

---
layout: preprint
#layout: review, 11pt
title: "RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R"
author: 
  - name: Carl Boettiger
    affiliation: cstar
    email: cboettig(at)gmail.com
    footnote: Corresponding author
  - name: Hilmar Lapp
    affiliation: NESCent
  - name: Scott Chamberlain
    affiliation: SimonFraser
  - name: Rutger Vos
    affiliation: NBC
address: 
  - code: cstar
    address: | 
      Center for Stock Assessment Research, 
      Department of Applied Math and Statistics, 
      University of California, Mail Stop SOE-2,
      Santa Cruz, CA 95064, USA
  - code: NESCent
    address: | 
      National Evolutionary Synthesis Center, Durham, NC, USA
  - code: SimonFraser
    address: |
      Department of Biology, Simon Fraser University, Burnaby, Canada
  - code: NBC
    address: | 
      Naturalis Biodiversity Center, Leiden, the Netherlands
abstract: | 
      1. NeXML promises to be the next generation of phylogenetic
      informatics data and metadata exchange formats, offering substantial
      improvements in reliability, extensibility, and richness over
      earlier standards such as NEXUS. In this paper we present the RNeXML
      package which provides a bridge between this rich and reliable
      data format and the extensive library of phylogenetic tools already
      available in R, with a particular emphasis on comparative methods.

>>>>

---
layout: preprint
#layout: review, 11pt
title: "RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R"
author: 
  - name: Carl Boettiger
    affiliation: cstar
    email: cboettig(at)gmail.com
    footnote: Corresponding author
  - name: Hilmar Lapp
    affiliation: NESCent
  - name: Scott Chamberlain
    affiliation: SimonFraser
  - name: Rutger Vos
    affiliation: NBC
address: 
  - code: cstar
    address: | 
      Center for Stock Assessment Research, 
      Department of Applied Math and Statistics, 
      University of California, Mail Stop SOE-2,
      Santa Cruz, CA 95064, USA
  - code: NESCent
    address: | 
      National Evolutionary Synthesis Center, Durham, NC, USA
  - code: SimonFraser
    address: |
      Department of Biology, Simon Fraser University, Burnaby, Canada
  - code: NBC
    address: | 
      Naturalis Biodiversity Center, Leiden, the Netherlands
abstract: | 
      1. NeXML is a new phylogenetic informatics data and metadata exchange 
      format that offers substantial improvements in reliability, extensibility, 
      and richness over earlier standards such as NEXUS. In this paper we present 
      the RNeXML package which provides a bridge between this rich and reliable
      data format and the extensive library of phylogenetic tools already
      available in R, with a particular emphasis on comparative methods.
